SpARC: Sparse Redundant Calibration

### 2016-07-18 paper.tex
some minor changes to document

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\by}{\bmath{y}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Redundant calibration}
In the case of a redundant array we can not only solve for the gains $\bg$ but also the redundant visibilities $\by$ themselves. Where $\by = [y_1,\cdots,y_R]$, $y_i$ denotes 
a unique redundant visibility and $R$ is the maximum value of the mapping $\phi_{ij}$. The reason we can now also solve for $\by$ is because we have reduced the number of 
unknowns from $N+B$ to $N+R$, where $N+R$ is now less than $B$ due to the array redundancy. We can now reformulate the calibration problem for an redundant array as follow:
\begin{equation}
\min_{\bz}\|\br\| = \min_{\bz}\|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg,\by]^T$.

\subsection{Jacobian derivation}
\subsection{Hessian derivation}
\begin{equation}
\boldsymbol{H} = 
\begin{bmatrix}
\boldsymbol{A} & \boldsymbol{B}\\
\boldsymbol{B}^* & \boldsymbol{A}
\end{bmatrix}
\end{equation}

@@

\begin{equation}
[\boldsymbol{C}]_{ij} = 
\begin{cases}
 \sum_{k \neq i} \left | g_k \right |^2 \left | y_{|i-k|} \right |^2 & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

\begin{equation}
[\boldsymbol{D}]_{ij} = 
\begin{cases}
 g_i y_j^*  \left | g_{i+j} \right |^2  & \textrm{if} ~ i<j\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

@@

\begin{equation}
[\boldsymbol{F}]_{ij} = 
\begin{cases}
 g_i g_j  \left | y_{|i-j|} \right |^2  & \textrm{if} ~ i \neq j\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

\begin{equation}
[\boldsymbol{G}]_{ij} = 
\begin{cases}
 g_i y_j  \left | g_{i-j} \right |^2  & \textrm{if} ~ i > j\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

@@

\begin{equation}
\mathcal{I}_i = \left\{pq|(q - p) = i \right\}
\end{equation}

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Redundant calibration}
In the case of a redundant array we can not only solve for the gains $\bg$ but we can also solve for the redundant unknown visibilities $\by$. Where $\by = [y_1,\cdots,y_R]$, $y_i$ denotes 
a unique redundant visibility and $R$ is the maximum value of the mapping $\phi_{ij}$. The reason we can now also solve for $\by$ is because we have reduced the number of 
unknowns from $N+B$ to $N+R$, where $N+R$ is now less than $B$ due to the array redundancy. We can now reformulate the calibration problem for an redundant array as follow:
\begin{equation}
\min_{\bz}\|\br\| = \min_{\bz}\|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg,\by]^T$.

If we now follow the same extension strategy of \citet{Smirnov2015} we can rewrite eq to
\begin{equation}
\min_{\breve{\bz}}\|\breve{\br}\| = \min_{\bz}\|\breve{\bd} - \breve{\bv}(\breve{\bz})\|, 
\end{equation}
where $\breve{\bz} = [\bz,\conj{\bz}]^T$ still need to define the remaining variables properly.

We can now solve the above equation by using least-squares, which entails deriving the Gauss-Newton (GN) and Levenberg-Marquerdt (LM) update rules.
(NEED TO WRITE THIS MUCH BETTER)

\begin{equation}
\bJ = \frac{\partial\bv}{\partial\bz}~\bJ^* = \frac{\partial \bv}{\partial \breve{\bz}} 
\end{equation}

\begin{equation}
\bJ = \begin{bmatrix}
       \bJ & \bJ^* \\
       \conj{\bJ^*} & \conj{\bJ}  
      \end{bmatrix}
\end{equation}

\begin{equation}
 \Delta \breve{\bz} = \begin{bmatrix}\Delta \bz\\ \Delta \conj{\bz} \end{bmatrix} = (\bJ^H\bJ)^{-1}\bJ^H\breve{\br_k}
\end{equation}

\begin{equation}
 \Delta \breve{\bz} = \begin{bmatrix}\Delta \bz\\ \Delta \conj{\bz} \end{bmatrix} = (\bJ^H\bJ + \lambda \bD)^{-1}\bJ^H\breve{\br_k}
\end{equation}

\subsection{Jacobian derivation}
\subsection{Hessian derivation}
\begin{equation}
\boldsymbol{H} = 
\begin{bmatrix}
\boldsymbol{A} & \boldsymbol{B}\\
\boldsymbol{B}^* & \boldsymbol{A}^*
\end{bmatrix}
\end{equation}

@@

\begin{equation}
[\boldsymbol{C}]_{ij} = 
\begin{cases}
 \sum_{k \neq i} \left | g_k \right |^2 \left | y_{\zeta_{ik}} \right |^2 & \textrm{if} ~ i=j\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

\begin{equation}
[\boldsymbol{D}]_{ij} = 
\begin{cases}
 g_i y_j^*  \left | g_{\psi_{ij}} \right |^2  & \textrm{if} ~ \psi_{ij}\neq0\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

@@

\begin{equation}
[\boldsymbol{F}]_{ij} = 
\begin{cases}
 g_i g_j  \left | y_{\zeta_{ij}} \right |^2  & \textrm{if} ~ (i \neq j)\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

\begin{equation}
[\boldsymbol{G}]_{ij} = 
\begin{cases}
 g_i y_j  \left | g_{\xi_{ij}} \right |^2  & \textrm{if} ~ (\xi_{ij}\neq0)\\
 0 & \textrm{otherwise}
\end{cases}
\end{equation}

@@

\begin{equation}
\mathcal{I}_i = \left\{pq\in\mathbb{N}^2|(\phi_{pq} = i) \right\}.
\end{equation}
